\Needspace{14\baselineskip}
\section{Method}
\label{sec:metodo}

This systematic review follows the methodology of
\citet{kitchenham2007guidelines} for systematic reviews in software
engineering, incorporating the updates of
\citet{kitchenham2013systematic}.
Reporting adopts the Software Engineering Guidelines for Reporting
Secondary Studies (SEGRESS)~\citep{kitchenham2023segress}, an adaptation
of PRISMA 2020~\citep{page2021prisma} for secondary studies in software
engineering.
The search strategy follows the PRISMA-S
extension~\citep{rethlefsen2021prismas}, and the full report follows the
27-item PRISMA 2020 checklist.

\subsection{Protocol and registration}
\label{sec:protocolo}

The protocol was drafted before the searches began.
Six amendments were logged during execution, refining eligibility
criteria and the extraction form.

\subsection{Eligibility criteria}
\label{sec:criterios}

Criteria were formulated under the PICo framework:
the \textbf{P}opulation comprises AI-based coding agents with mechanisms
for persisting knowledge across sessions;
the \textbf{I}nterest covers persistence architectures, their
effectiveness, and their cost-efficiency;
the \textbf{Co}ntext includes empirical evaluations, benchmarks, and
proposals of tools or frameworks.

\autoref{tab:criterios} lists the inclusion and exclusion criteria.
IC1 requires an explicit component that stores and reuses knowledge
across sessions or sequential tasks;
systems that merely retrieve context within a single session do not
satisfy this criterion.
IC2 sets a minimum floor for empirical evaluation: at least two tasks
and quantitative metrics.
EC2 acts as a conditional rule: papers on generic LLM agents were
included when the evaluation contained software engineering benchmarks.
The coverage period spans publications from 2023 to March 2026.

\begin{table}[htbp]
  \centering
  \caption{Eligibility criteria.}
  \label{tab:criterios}
  \begin{tabularx}{\textwidth}{l l X}
    \toprule
    ID  & Type & Description \\
    \midrule
    IC1 & Inclusion & Proposes or evaluates a mechanism to persist
      knowledge across sessions in AI-based coding agents \\
    IC2 & Inclusion & Reports empirical results with at least two
      tasks and quantitative metrics \\
    IC3 & Inclusion & Published between 2023 and March 2026 \\
    IC4 & Inclusion & Written in English or Portuguese \\
    IC5 & Inclusion & Peer-reviewed publication or preprint with
      identifiable authors and institutions \\
    \midrule
    EC1 & Exclusion & Addresses only RAG or intra-session context
      retrieval, with no cross-session persistence \\
    EC2 & Exclusion & Addresses only natural-language tasks, with no
      evaluation on software engineering benchmarks \\
    EC3 & Exclusion & Evaluation limited to anecdotal examples \\
    EC4 & Exclusion & Tutorial, editorial, or position paper without
      technical contribution \\
    EC5 & Exclusion & Duplicate version or superseded by a later
      version from the same authors \\
    \bottomrule
  \end{tabularx}
\end{table}

\subsection{Information sources}
\label{sec:fontes}

Searches ran on two databases that support reproducible Boolean queries:
Scopus (via API) and arXiv (via REST API with full pagination).
The two-database strategy complemented by citation chasing is empirically
validated by \citet{mourao2020hybrid}, who showed that Scopus combined
with snowballing achieves recall comparable to searches across four or
more databases for software engineering systematic reviews.
IEEE Xplore was not searched separately because Scopus fully indexes its
proceedings and journals.

The search was supplemented by forward and backward citation chasing via
Semantic Scholar, starting from seven seed papers chosen for their
architectural diversity and for being the most cited in the
subfield~\citep{du2026memory,joshi2025swebenchcl,wang2026codemem,deng2026memcoder,wu2025gcc,wang2026improving,lindenbauer2025ctimrover}.
One of the seven seed papers (CodeMEM) was not captured by the search
strings because it uses vocabulary outside the string terms;
its manual addition to the screening pool was recorded as a protocol
amendment.

\subsection{Search strategy}
\label{sec:busca}

The search string combines three conceptual blocks joined by AND
(\autoref{tab:strings-busca}): AI agents for code (C1, 12 terms),
memory and persistence (C2, 13 terms), and the software engineering
domain (C3, 8 terms).
Terms within each block are joined by OR.

\begin{table}[htbp]
  \centering
  \caption{Search terms organised by conceptual block.
           Inter-block operator: C1~AND~C2~AND~C3;
           intra-block operator: OR.}
  \label{tab:strings-busca}
  \small
  \begin{tabularx}{\textwidth}{@{}
    >{\raggedright\arraybackslash}p{2.8cm}
    X @{}}
    \toprule
    Block & Terms \\
    \midrule
    C1 --- AI agents for code (12)
    & \texttt{"LLM agent"},
      \texttt{"AI coding agent"},
      \texttt{"software engineering agent"},
      \texttt{"autonomous coding"},
      \texttt{"code agent"},
      \texttt{"LLM-based software"},
      \texttt{"AI-assisted software"},
      \texttt{"coding assistant"},
      \texttt{"language agent"},
      \texttt{"code assistant"},
      \texttt{"agentic coding"},
      \texttt{"SWE agent"} \\
    \addlinespace
    C2 --- Memory and persistence (13)
    & \texttt{"memory"},
      \texttt{"knowledge persistence"},
      \texttt{"experience"},
      \texttt{"context management"},
      \texttt{"long-term memory"},
      \texttt{"episodic memory"},
      \texttt{"knowledge reuse"},
      \texttt{"continual learning"},
      \texttt{"experience replay"},
      \texttt{"memory-augmented"},
      \texttt{"persistent memory"},
      \texttt{"persistent context"},
      \texttt{"cross-task"} \\
    \addlinespace
    C3 --- Software engineering (8)
    & \texttt{"software engineering"},
      \texttt{"software development"},
      \texttt{"code generation"},
      \texttt{"bug fix"},
      \texttt{"code repair"},
      \texttt{"repository"},
      \texttt{"software maintenance"},
      \texttt{"issue resolution"} \\
    \bottomrule
  \end{tabularx}
\end{table}

In Scopus, the three blocks operate on title, abstract, and keywords
(\texttt{TITLE-ABS-KEY}) with the temporal filter
\texttt{PUBYEAR\,>\,2022}.
In arXiv, C1 and C2 operate on the abstract (\texttt{abs:}) and, for
four terms of C1, also on the title (\texttt{ti:}); block C3 is
replaced by the category filter \texttt{cs.SE}, \texttt{cs.AI}, and
\texttt{cs.CL}, with post-search filter \texttt{--year-from\,2023}.
The exact strings per database, in each API's native syntax, are
available in the replication package
(DOI: 10.5281/zenodo.19463131).

Before execution, the strings underwent audit against eight comparable
SLRs, 16 known systems, and ten alternative term formulations, resulting
in the addition of six terms and coverage of six of the seven seed
papers.
The single unretrieved seed paper (CodeMEM) uses vocabulary outside the
string terms and was added manually.

\autoref{tab:busca} lists results per source.
Searches ran on 25 March 2026.
Citation chasing identified 186 unique records (8 forward, 178 backward).
After consolidation and deduplication, the initial screening pool
contains 1,111 records.

\begin{table}[htbp]
  \centering
  \caption{Search results per source.}
  \label{tab:busca}
  \begin{tabular}{l r}
    \toprule
    Source & Records \\
    \midrule
    Scopus              &    39 \\
    arXiv               &   968 \\
    Forward citations   &     8 \\
    Backward citations  &   178 \\
    Manual              &     1 \\
    \midrule
    Raw total           & 1,194 \\
    Duplicates removed  & $-83$ \\
    \textbf{Screening pool} & \textbf{1,111} \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Selection process}
\label{sec:selecao}

Selection proceeded in two phases.
The researcher screened the 1,111 records by title and abstract,
applying the IC/EC criteria.
Uncertain records advanced to the next phase.
Of the 1,111 screened records, 1,060 were excluded and 51 advanced to
full-text assessment.

Full-text reading of the 51 candidates yielded 23 exclusions.
Of the 23 excluded, 12 were removed under EC2 (LLM agents without
software engineering evaluation) and 11 under the combined IC1/EC1 rule
(intra-session retrieval without cross-session persistence).
Three borderline cases were accepted with documented rationale.
At the end, 28 studies were included for data extraction.

\subsection{Data extraction}
\label{sec:extracao}

Data were extracted using a 37-field form organised into seven
categories, with emphasis on persistence architecture (8 fields) and
cost and efficiency (6 fields), which map directly to the research
questions.
Sixteen fields use a controlled vocabulary with predefined values.
Fields with no available data receive NR (not reported) when the paper
does not mention the datum or NA (not applicable) when the field does
not apply to the system, a convention recorded as a protocol amendment.

Each paper was read, its data logged on the form, and the values
verified afterwards.
Validation included programmatic checks on 448 enum values and a
spot-check of 40 interpretive fields across ten papers.
The final error rate was below 1\%, corresponding to eight corrections
out of 1{,}036 extracted values (28 papers $\times$ 37 fields).

\subsection{Quality assessment}
\label{sec:qualidade}

Study quality was assessed with a six-item checklist adapted from
\citet{kitchenham2007guidelines}: (Q1) clearly defined objectives,
(Q2) appropriate evaluation method, (Q3) threats to validity discussed,
(Q4) results based on empirical data, (Q5) context described for
replication, and (Q6) clearly defined metrics.
Each item received a score of 0, 0.5, or 1, up to a maximum of 6.0.

Scores range from 2.0 to 6.0, with a median of 5.0.
Twenty-six of the 28 studies (93\%) scored at or above 4.0.
The two studies scoring below
3.0~\citep{bui2026opendev,du2026memory} contribute only qualitative
descriptions and do not affect the quantitative findings, as verified in
the sensitivity analysis (\autoref{sec:resultados}).
For calibration, eight papers were re-assessed after the full extraction.

\subsection{Synthesis methods}
\label{sec:sintese}

The synthesis is narrative, organised thematically by the five secondary
questions (SQ1 through SQ5).
Meta-analysis was ruled out because of heterogeneity in benchmarks,
base models, and experimental conditions across studies.
Since the synthesis is narrative, formal effect measures (e.g., odds
ratio, standardized mean difference) do not apply.
Reported measures are limited to Pass@1 and absolute variation in
percentage points (\textit{delta-pp}).

Two sensitivity analyses were conducted:
(S1) re-synthesis restricted to the five studies published in
peer-reviewed venues, to check whether the findings hold without
preprints;
(S2) exclusion of the two studies scoring below 3.0, to gauge the
impact on quantitative findings.

Formal publication-bias assessment is not applicable to narrative
synthesis~\citep{page2021prisma}.
The preprint-dominated corpus (82\%) is acknowledged as a potential
source of bias and discussed in the limitations.
Certainty of evidence was rated qualitatively per finding:
high (multiple studies with quality $\geq$~4/6 converge),
moderate (few studies or variable quality), and
low (finding based on a single or low-quality
study)~\citep{kitchenham2023segress}.
