\section{Architecture Classification Ledger}
\label{ap:classification-ledger}

This appendix reports the coded values used for the SQ1 taxonomy and
for inclusion in the SQ3 and SQ4 syntheses.
It is a compact audit ledger for the 24 architecture studies; the four
contextual sources are excluded from this table.
For SQ3, ``pp'' marks inclusion in the percentage-point synthesis,
``sep.'' marks studies discussed separately because their metrics are
not comparable in percentage points, and ``excl.'' marks studies
excluded from the SQ3 percentage-point synthesis.
For SQ4, ``detailed'' marks monetary cost with supporting detail,
``partial'' marks token or cost evidence without complete
cost accounting, and ``none'' marks no usable cost data.

\scriptsize
\setlength{\tabcolsep}{2pt}
\begin{longtable}{@{}
  >{\raggedright\arraybackslash}p{2.15cm}
  >{\raggedright\arraybackslash}p{2.05cm}
  >{\raggedright\arraybackslash}p{1.35cm}
  >{\raggedright\arraybackslash}p{1.45cm}
  >{\raggedright\arraybackslash}p{1.2cm}
  >{\raggedright\arraybackslash}p{1.55cm}
  >{\centering\arraybackslash}p{0.75cm}
  >{\centering\arraybackslash}p{0.95cm}
@{}}
  \caption{Classification ledger for the 24 architecture studies.}
  \label{tab:classification-ledger} \\
  \toprule
  Study & Family & Scope & Substrate & Control & Retrieval & SQ3 & SQ4 \\
  \midrule
  \endfirsthead
  \toprule
  Study & Family & Scope & Substrate & Control & Retrieval & SQ3 & SQ4 \\
  \midrule
  \endhead
  \bottomrule
  \endfoot
  Bui (OpenDev) & Text notes & Hybrid & Text & LLM & Hybrid & excl. & none \\
  Chen (SWE-Exp) & Experience bank & Hybrid & Structured & LLM & Hybrid & pp & detailed \\
  Deng (MemCoder) & Experience bank & Hybrid & Structured & LLM & Hybrid & pp & none \\
  Dong (KernelBlaster) & Hierarchical/state KB & Hybrid & Structured & Learned & State match & sep. & partial \\
  Guo (EET) & Experience bank & Episodic & Structured & LLM & TF-IDF top-1 & pp & detailed \\
  Hosain (Xolver) & Hybrid & Hybrid & Text & LLM & Hybrid & excl. & partial \\
  Li (GBT) & Executable substrate & Procedural & Executable & Heuristic & Other & pp & partial \\
  Lindenbauer (CTIM-Rover) & Experience bank & Episodic & Text & Heuristic & Embeddings & pp & none \\
  Nadafian (KAPSO) & Hybrid & Hybrid & Hybrid & LLM & Hybrid & pp & partial \\
  Qian (IER) & Experience bank & Procedural & Text & Heuristic & Embeddings & excl. & none \\
  Shen (TALM) & Experience bank & Hybrid & Hybrid & Heuristic & Embeddings & pp & partial \\
  Shen (Structurally) & Experience bank & Procedural & Structured & Heuristic & Hybrid & pp & none \\
  Su (Learn-by-Interact) & Experience bank & Episodic & Text & Heuristic & Hybrid & pp & partial \\
  Tablan (Spark) & Experience bank & Hybrid & Hybrid & LLM & Hybrid & sep. & none \\
  Vasilopoulos (Codified) & Hybrid & Hybrid & Text & Heuristic & Hybrid & excl. & none \\
  Wang (RepoMem) & Repository-history memory & Hybrid & Hybrid & Heuristic & BM25 & pp & partial \\
  Wang (CodeMEM) & AST-guided & Hybrid & Hybrid & LLM & AST intersection & pp & partial \\
  Wang (MemGovern) & Experience bank & Semantic & Structured & LLM & Hybrid & pp & detailed \\
  Wong (CCA) & Hybrid & Hybrid & Text & LLM & Hybrid & pp & partial \\
  Wu (GCC) & Git-style version-control memory & Hybrid & Text & LLM & Hybrid & pp & detailed \\
  Xia (Live-SWE-Agent) & Executable substrate (task-local) & Procedural & Executable & LLM & Full load & pp & detailed \\
  Zhang (AccelOpt) & Experience bank & Episodic & Text & Heuristic & Full load & excl. & detailed \\
  Zhang (DGM) & Executable substrate & Procedural & Executable & Learned & Other & pp & none \\
  Zhou (ToM-SWE) & Hybrid & Hybrid & Structured & LLM & BM25 & pp & detailed \\
\end{longtable}
\normalsize
