\Needspace{14\baselineskip}
\section{Conclusion}
\label{sec:conclusion}

This systematic review mapped 28 studies on knowledge persistence in
AI-based coding agents, all published from 2024 onwards.
The field is recent and predominantly composed of preprints (82\%);
the 28 included studies comprise 24 architecture proposals and four
contextual sources (one analytical survey, two benchmark proposals, and
one security evaluation).
Controlled no-persistence comparisons are mostly positive but not
uniformly so: 18 of the 19 architecture studies with a controlled
baseline report positive aggregate gains, while CTIM-Rover reports
negative results across all CTIM configurations.
The evidence also shows diminishing returns on strong baselines,
adverse or cautionary findings related to persistence in nine of the
28 included studies, and persistent gaps in cost reporting.

The five secondary questions received answers with differing degrees of
certainty.
For the taxonomy (SQ1), experience banks predominate among the 24
architecture studies (46\%), the LLM acts as the controller in 54\% of
the systems, and hybrid temporal scope is the most frequent (58\%).
On evaluation (SQ2), SWE-bench Verified is the most frequent
benchmark, appearing in 13 of the 24 studies with benchmark evaluation
(54\%), but comparability is limited by heterogeneous model choices
and differences in framework and experimental setup.
Performance gains (SQ3) are mostly positive: 18 of the 19
architecture studies with a controlled no-persistence baseline report
positive aggregate results in their main controlled comparison, while
CTIM-Rover reports negative results;
within the SWE-bench Verified subset ($n=12$, including CTIM-Rover) the
median gain is 6.5~pp, and across the 18 comparable comparisons the
median is 7.8~pp, with reported gains ranging from $-$2.0 to
+39.0~pp.
For cost (SQ4), eight of 24 architecture studies (33\%) report no cost
data, and the memory impact is bimodal: systems that replace context
reduce tokens, while systems that add context raise cost by
approximately 5 to 21\%.
On complexity and effectiveness (SQ5), nine of the 28 included studies
(32\%) report adverse or cautionary findings related to persistence;
four report direct performance drops in their main or coded adverse
comparison (retrieval noise, backend redundancy with follow-up decay,
or model-dependent overhead), and TALM reports sub-benchmark drops on
HumanEval when memory is enabled;
the corpus contains no controlled evidence that isolates architectural
complexity as a cause of larger gains.

None of the 28 studies compares persistence architectures directly.
This absence, combined with cost underreporting and the uncertainty
about the role of architectural complexity, prevents informed decisions
about which approach to adopt in each context.
The most critical gap is the absence of head-to-head comparisons.
Closing it requires a comparative experiment that evaluates at least
three representative architectures under a shared benchmark, a fixed
model backbone, and integrated per-task cost analysis.
